Gravitational wave sources in our Galactic backyard: LISA predictions for BH and NS binaries

### 2021-06-02 paper/tex/sections/introduction.tex

Since the first direct detection of gravitational waves by the LIGO scientific collaboration \citep{Abbott+2016_first_detection}, the number of black hole (BH) binaries and neutron star (NS) binaries detected by ground-based detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}. The detection of the mergers of these binaries have offered exciting insights into the evolution and endpoints of massive stars.

>>>>

Since the first direct detection of gravitational waves by the LIGO scientific collaboration \citep{Abbott+2016_first_detection}, the number of black hole (BH) binaries and neutron star (NS) binaries detected by ground-based detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}. The detection of the mergers of these binaries have offered exciting insights into the evolution and endpoints of massive stars.
\floor{I would change it to something like: Since the first direct observation of gravitational waves by the LIGO scientific collaboration in 2015 \citep{Abbott+2016_first_detection}, the number of black hole (BH) and neutron star (NS) binaries observed by ground-based gravitational-wave detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}, offering exciting insights into the formation, lives and deaths of massive (binary) stars (e.g. CITE GWTC-2 Population inference paper).}
